%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
%\colorlet{awesome}{awesome-emerald}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Berkay}{ Ersever}
\recipient{ESPA - Game Development Internship}{Glasgow, Scotland}
\address{Istanbul, Turkey}
\mobile{(+90) 536-691-91-73} 
%%% Social
\email{berkayersever@sabanciuniv.edu}
\homepage{berkayersever.github.io}
\github{berkayersever}
\linkedin{berkayersever}
%%% Optionals
\position{Software Engineer{\enskip\cdotp\enskip}Game Developer}
\quote{Avant-garde mixer of art, mathematics, science and technology. Complex problem-solver with an
analytical and driven mindset. Full-stack developer using MERN technology. Passionate video game builder using Unity.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\letterdate{\today}
\lettertitle{Job Application for Game Development Internship}
\letteropening{Dear ESPA,}
\letterclosing{Sincerely,}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Berkay Ersever~~~·~~~Cover Letter}
  {ESPA}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
I am an enthusiastic software engineer who loves to learn new skills, redesign the ways to obtain them and show the world what you can do with them. I own a spirited interest in technological advances and flamboyant ways in which you can create solutions based on these. I previously worked for "Philips Turkey" company, developed a full stack application to keep track of maintenance records of the medical devices using MongoDB, React, Node.js and Express.
Improved the MongoDB query performance by 20\% and redesigned the user interface to achieve an easy to use application.

\cvparagraph{Why Game Development?}
I'm looking for an organic environment with fluid teamwork and mutual cooperation in diverse areas of knowledge. Game Development draws my attention because it is willing to take risks and innovate in fields that others leave behind. I want to work in a place where my job becomes meaningful to others, a place where I can help people reach further and innovate more.

\cvparagraph{Why Me?}
 Coding it's my daily driver. I love helping others and find extremely necessary in doing so. I have designed and implemented an educational web based parametric game against phishing attacks using Unity for the game development, used Node.js for the backend part and Koa as a web framework connected to a PostgreSQL database. Coordinated with two group members while developing the graduation project.
 
\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
